Draft Report

### 2020-11-18 DraftReport.Rmd
comment add in model2, some polishing. p-value of poverty percentage update in conclusion part, 0.06** to 0.5755

This question can be broken up into two distinctive areas of investigation. The first and primary area of investigation involves how the COVID case rate is affected by population metrics. For this, the key variables are COVID case rate per 100,000 residents and the population density per square mile. This will provide an initial understanding in the relationship between the spread of the virus and how densely populated a state is. Following this, the analysis considers variables that address the make-up of these populations, specifically focusing on the distribution of demographics such as race/ethnicity and age. In order to account for the varying population sizes across the states, the variables are operationalized by specifically looking at variables that contain a rate, in order to standardize across the samples. In this sense, the analysis quantifies the spread of COVID by leveraging the COVID case rate per 100,000 rate, and for population demographics it investigates the percentage distribution of the race/ethnicity and age categories (e.g., White % of Total Population).

@@

Currently, Case rate per 100,000 is chosen as a dependent variable to represent the pandemic status in each state. Variables such as population density per square miles, unemployed (2018)/percentage living under the federal poverty line (2018), white/black percentage of of total Population, percentage of seniors(65+), and mask mandate policies are chosen as candidate covariates to explore potential relationships between pandemic status demographic characteristics, economic status, racial composition, and state policy.

@@

Several transformations have been made for variables a Population density per square miles and White % of Total Population. Population density is extremely skewed due to the high population density of the District of Columbia.  A logarithm transformation of this variable is of more uniform distribution. In addition, the square of the white percentage of the total population is of a distribution closer to the normal distribution. It also represents the chance that the interaction happens between two white people in practice.

@@

@@

According to the regression results, no coefficients regarding the demographic variables investigated in model 2 are statistically significant. There is no statistically meaningful relationship that could be concluded by now.

### Model 2 Regression

@@

@@

Conversely, the hypotheses that population and demographics would have an effect on the COVID case rate was unable to be accepted. Although upon investigating the poverty line percentage variable in model 2 there was a detection of notable adjacency to a significant result (and an actual significant result when using the `stargazer` package to compute the regression table) with a coefficient value of 0.06286, it was not enough to be truly significant and reject the null hypothesis. Similarly, the relationship of race/ethnicity as well as age on case rate was also insignificant with no apparent correlation.

>>>>

This question can be broken up into two distinctive areas of investigation. The first and primary area of investigation involves how the COVID case rate is affected by population metrics. For this, the key variables are COVID case rate per 100,000 residents and the population density per square mile. This will provide an initial understanding in the relationship between the spread of the virus and how densely populated a state is. Following this, the analysis considers variables that address the make-up of these populations, specifically focusing on the distribution of demographics such as race/ethnicity and age. In order to account for the varying population sizes across the states, the variables are operationalized by specifically looking at variables that contain a rate, in order to standardize across the samples. In this sense, the analysis quantifies the spread of COVID by leveraging the COVID case rate per 100,000 rate, and for population demographics it investigates the percentage distribution of the race/ethnicity and age categories (e.g., white percentage of total population).

@@

Currently, Case rate per 100,000 is chosen as a dependent variable to represent the pandemic status in each state. Variables such as population density per square miles, unemployed percentage(2018)/percentage living under the federal poverty line(2018), white/black percentage of total population, percentage of seniors(65+), and mask mandate policies are chosen as candidate covariates to explore potential relationships between pandemic status demographic characteristics, economic status, racial composition, and state policy.

@@

Several transformations have been made for variables as population density per square miles and white percentage of total population. Population density is extremely skewed due to the high population density of the District of Columbia. A logarithm transformation of this variable is of more uniform distribution. In addition, the square of the white percentage of the total population is of a distribution closer to the normal distribution. It also represents the chance that the interaction happens between two white people in practice.

@@

For model 2, state demographic information regarding racial composition(white percentage of total population /Black Percentage of Total Population), economic status(unemployed percentage/poverty percentage), and population seniors percentage was investigated to explore its potential connection to the COVID pandemic status.

@@

### Model 2 Regression
The regression models regarding the demographic variables discussed previously are listed as below.However, no coefficients regarding these variables in model 2 are statistically significant.

@@

From the results of the regression, none of the coefficients of investigated variables in model 2 are significant (p-value < 0.05). Among these regression coefficient tests,  the p-value regarding the poverty percentage variable is the lowest (0.05755).  In addition, its positive estimated coefficient is consistent with the statement that low-income communities are at high pandemic risk claimed by mainstream media these days.

@@

Conversely, the hypotheses that population and demographics would have an effect on the COVID case rate was unable to be accepted. Although upon investigating the poverty percentage variable in model 2 there was a detection of notable adjacency to a significant result (and an actual significant result when using the `stargazer` package to compute the regression table) with a p-value of 0.05755, it was not enough to be truly significant and reject the null hypothesis. Similarly, the relationship of race/ethnicity as well as age on case rate was also insignificant with no apparent correlation.
